\vspace{1.0cm} \LARGE \bf Revealing the competitive dynamics of influenza viruses through evolutionary cartography \\ or \\ Charting antigenic drift and evolutionary success of seasonal influenza lineages

### 2013-01-25 flux.tex
Fix compile.

%%% TITLE %%%
\title{\vspace{1.0cm} \Large \bf 
Revealing the competitive dynamics of influenza viruses through evolutionary cartography \\
or \\
Charting antigenic drift and evolutionary success of seasonal influenza lineages \\
or \\
Integrating influenza antigenic dynamics with molecular evolution \\
or \\
Cartographic analysis of antigenic dynamics and evolutionary success of seasonal influenza lineages \\
or \\
Integrating antigenic cartography and molecular evolution to characterize predictors of evolutionary success of seasonal influenza lineages 
or \\
Predicting the evolutionary success of seasonal influenza lineages through the integration of antigenic cartography and molecular evolution

}

@@

Before 2009, there were four major clades of influenza circulating within the human population: A/H3N2, A/H1N1, B/Victoria and B/Yamagata. 
In the case of influenza A, subtypes A/H3N2 and A/H1N1 refer to the genes, hemagglutinin (H or HA) and neuraminidase (N or NA), that are primarily responsible for the antigenic character of a strain. 
In the case of influenza B, B/Vic and B/Yam refer to antigenically distinct lineages which diverged from a single one prior to 1980 \cite{Rota92}.
Mutations to the HA1 region of the hemagglutinin protein are thought to drive the majority of antigenic drift in the influenza virus \cite{Nelson07NatRevGenet}. 
Experimental characterization of antigenic phenotype is possible through the hemagglutination inhibition (HI) assay \cite{Hirst43}, which measures the cross-reactivity of one virus strain to serum raised against another strain through challenge or vaccination. 
Sera from older strains react poorly with more evolved viruses resulting in new strains having a transmission advantage over previously established strains.
HI assays have shown there to be little to no cross-reactivity between influenza clades A/H3N2, A/H1N1, B/Vic and B/Yam \cite{Hay01}.

>>>>

%%% TITLE %%%
\title{\vspace{1.0cm} \Large \bf 
Revealing the competitive dynamics of influenza viruses through evolutionary cartography \\
or \\
Charting antigenic drift and evolutionary success of seasonal influenza lineages \\
or \\
Integrating influenza antigenic dynamics with molecular evolution \\
or \\
Cartographic analysis of antigenic dynamics and evolutionary success of seasonal influenza lineages \\
or \\
Integrating antigenic cartography and molecular evolution to characterize predictors of evolutionary success of seasonal influenza lineages \\
or \\
Predicting the evolutionary success of seasonal influenza lineages through the integration of antigenic cartography and molecular evolution   
}

@@

Before 2009, there were four major clades of influenza circulating within the human population: A/H3N2, A/H1N1, B/Victoria and B/Yamagata. 
In the case of influenza A, subtypes A/H3N2 and A/H1N1 refer to the genes, hemagglutinin (H or HA) and neuraminidase (N or NA), that are primarily responsible for the antigenic character of a strain. 
In the case of influenza B, B/Vic and B/Yam refer to antigenically distinct lineages which diverged from a single lineage prior to 1980 \cite{Rota92}.
Mutations to the HA1 region of the hemagglutinin protein are thought to drive the majority of antigenic drift in the influenza virus \cite{Nelson07NatRevGenet}. 
Experimental characterization of antigenic phenotype is possible through the hemagglutination inhibition (HI) assay \cite{Hirst43}, which measures the cross-reactivity of one virus strain to serum raised against another strain through challenge or vaccination. 
Sera from older strains react poorly with more evolved viruses resulting in new strains having a transmission advantage over previously established strains.
HI assays have shown there to be little to no cross-reactivity between influenza clades A/H3N2, A/H1N1, B/Vic and B/Yam \cite{Hay01}.
